---
title: "K Nearest Neighbor Tutorial"
author: "Congxin (David) Xu"
date: "12/11/2020"
output: html_document
---

```{r Setup, include=FALSE}
knitr::opts_chunk$set(error=TRUE,           # Keep compiling upon error
                      collapse=FALSE,       # collapse by default
                      echo=TRUE,            # echo code by default
                      comment = "#>",       # change comment character
                      fig.width = 5,        # set figure width
                      fig.align = "center", # set figure position
                      out.width = "49%",    # set width of displayed images
                      warning=TRUE,         # show R warnings
                      message=TRUE)         # show R messages
options(dplyr.summarise.inform = FALSE)     # ignore message about group structure
```


```{css Solution-Region, echo=FALSE}
.solution {
  background-color: #232D4B10;
  border-style: solid;
  border-color: #232D4B;
  padding: .5em;
  margin: 20px
}
```


## Description

This tutorial is going to discuss how to implement K Nearest Neighbor model in `R`. 

## Package Dependency

- [`tidyverse`](https://www.tidyverse.org/)
  - We will mainly use `tidyverse` for data manipulation (`dplyr`) and visualization (`ggplot2`). 
- [`FNN`](https://cran.r-project.org/web/packages/FNN/FNN.pdf)
  - Title: Fast Nearest Neighbor Search Algorithms and Applications
  - This is package that contains the `knn.reg()` function that will performn the K-Nearest-Neighbor regression


<div class="solution">
    
```{r Packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(FNN)
```

<div>

## Data

The data we used here is the 

```{r Data,}
train <- read_csv('.\\Data\\realestate-train.csv')
```












